%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{%
  colorlinks=true,% hyperlinks will be black
  urlcolor=blue,
}
\usepackage{multicol}
\usepackage[skip=5pt]{parskip}

% \setstretch{1.25}

\title{Academic CV}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft2.5\hoffset\centerline{\LARGE\bf Anjali Pal} % Your name at the top

 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
%\moveleft.5\hoffset\centerline{45 Lansing St Apt 2612} % Your address
%\moveleft.5\hoffset\centerline{San Francisco, San Francisco 94105}
%\moveleft.5\hoffset\centerline{(770) 401-6678}
%\moveleft.5\hoffset\centerline{josheppinette@icloud.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 

\section{Contact Information}
\href{mailto:anjalip@cs.washington.edu}{anjalip@cs.washington.edu}

\href{https://github.com/ajpal}{https://github.com/ajpal}

% \href{https://www.linkedin.com/in/anjalipal/}{https://www.linkedin.com/in/anjalipal/}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education} 

{\textbf{University of Washington}} Seattle, WA \hfill 2022 - Present \\
Ph. D. in Computer Science

{\textbf{Brown University}} Providence, RI \hfill 2013 - 2017  \\
Sc. B. in Computer Science

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\section{Publications}
{\textit{Equality Saturation Theory Exploration à la Carte}} \hfill OOPSLA 2023 \\
 \textbf{Anjali Pal}, Brett Saiki, Ryan Tjoa, Cynthia Richey, Amy Zhu, \\
 Oliver Flatt, Max Willsey, Zachary Tatlock, Chandrakana Nandi.

 
%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{Research Experience}
{\textbf{University of Washington}} \hfill Winter 2022 - Present \\ 
\textit{Advised by Zachary Tatlock}

\textsc{Poach}. A persistent model for e-graphs that enables reusing analyses and intermediate results across queries.

\textsc{Eggcc}. A compiler for imperative programs powered by e-graphs and a novel extraction algorithm that ensures the extracted program obeys effect-ordering constraints without the use of external solvers. 

\textsc{Enumo}. A domain-specific language for programmable theory exploration that enables rule inference in domains without decidable equality and scales well to deep rules and large domains. \\

{\textbf{Sandia National Laboratories}} \hfill Summer 2024 - Summer 2025 \\
\textit{Advised by John Bender}

Contributed to formally-verified compiler for concurrent programs, implemented in Rocq. Implemented backwards-simulation proof demonstrating equivalence between concurrent semantics and single-threaded semantics. \\

{\textbf{Brown University}} \hfill Spring 2016 \\
\textit{Advised by Shriram Krishnamurthi}

Used Liquid Haskell refinement types to statically analyze R programs with matrix operations and surface matrix arithmetic errors as static type errors.

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Teaching Experience}
{\textbf{Programming Languages}}, UW, Instructor \hfill Summer 2025

{\textbf{Programming Languages}}, UW, Co-Instructor \hfill Fall 2024

{\textbf{Software Design \& Implementation}}, UW, TA \hfill Winter 2024

{\textbf{Grad. Programming Languages}}, UW, TA \hfill Winter 2023

{\textbf{First Byte of Computer Science}}, Brown University, TA \hfill Spring 2017

{\textbf{Programming Languages}}, Brown University, Head TA \hfill Fall 2016

{\textbf{Logic for Systems}}, Brown University, TA \hfill Spring 2016

{\textbf{Intro. Functional Programming}}, Brown University, Head TA \hfill Fall 2015

{\textbf{Intro. Object Oriented Programming}}, Brown University, TA \hfill Spring 2015

{\textbf{Intro. Functional Programming}}, Brown University, TA \hfill Fall 2014

%----------------------------------------------------------------------------------------
%	TALKS SECTION
%----------------------------------------------------------------------------------------

\section{Invited Talks}
{\textbf{Fast and Flexible Program Optimization with E-Graphs}} \hfill Spring 2026 \\
\textit{Reed College, Department Seminar} \\

{\textbf{Fast and Flexible Program Optimization with E-Graphs}} \hfill Spring 2026 \\
\textit{Williams College, Department Seminar} \\

{\textbf{Flexible Theory Exploration}} \hfill Spring 2025 \\
\textit{Whitman College, Department Seminar}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}
{\textbf{Code.org}, Software Engineer} \hfill 2019 - 2022 \\
Full-stack developer on block programming environments for K-12 students. Led engineering and product efforts across courses reaching millions of students. \\

{\textbf{Google}, Software Engineer} \hfill 2017 - 2019 \\
\textit{Cloud Storage Security \& Privacy} \\
Implemented a FlumeJava pipeline to analyze object metadata in preparation for major metadata migration. \par
\textit{Android Maps} \\
Implemented features to provide fresher data on the Maps directions screen for limited connection and low-bandwidth settings. \par

%----------------------------------------------------------------------------------------
%	SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{Service \& Outreach}
{\textbf{PNW PLSE }} \hfill Spring 2026\\ 
\textit{Co-Chair}

{\textbf{UW Pre-Application Mentorship Service}} \hfill Fall 2024\\ 
\textit{Co-Chair}

{\textbf{PNW PLSE }} \hfill Spring 2025\\ 
\textit{Co-Chair}

{\textbf{UW Pre-Application Mentorship Service}} \hfill Fall 2024\\ 
\textit{Mentor}

{\textbf{PNW PLSE }} \hfill Spring 2024\\ 
\textit{Co-Chair}

{\textbf{SPLASH OOPSLA 2024}} \hfill Winter 2024 \\
\textit{Artifcact Evaluation Committee}

{\textbf{PNW PLSE}} \hfill Spring 2023 \\
\textit{Co-Chair}

{\textbf{Rainier Scholars}} \hfill 2018 - 2020 \\
\textit{Lecturer}

{\textbf{Google CS Summer Institute}} \hfill Summer 2018 \\
\textit{Teaching Assistant}

{\textbf{Brown University Women in CS}} \hfill 2015 - 2017 \\
\textit{Peer Mentor}


\end{resume}
\end{document}